---
title: "AgrodiversityData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AgrodiversityData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Getting started with **AgrodiversityData**

### Install and load the package
```{r setup}
library(AgrodiversityData)
```

### About the package
The agrodiversityData package provides datasets of the 3 year continental scale Agrodiversity experiment that investigated plant diversity and ecosystem functions in intensively-managed grassland communities across 17 countries. It was intended to see whether the experimental increase in plant diversity can change the grassland outcomes like total biomass, forage quality, nitrogen yield, weed supression etc. 

### Datasets included in the DImodels package
There are nine datasets included in the AgrodiversityData package: site, soil, forage1, forage2, biomass1, biomass2, weather1, weather2 and combined. Details about each of them is available in the corresponding help files. 

This vignette focuses on the descriptions of combined dataset

### The combined dataset
```{r}
data("combined")
dim(combined)
```

### To obtain the summary statistics for annual harvest dry matter yield
```{r}
summary(combined$an_yield)
```

```{r}
# To create a new variable, type= Mixture and Monoculture
library(dplyr)
combined1<-combined%>%mutate(type=ifelse((g1==1&g2==0&l1==0&l2==0)|(g1==0&g2==1&l1==0&l2==0)|(g1==0&g2==0&l1==1&l2==0)|(g1==0&g2==0&l1==0&l2==1),"Mono","Mix"))
levels(combined1$type)=list(Mixture="Mix",Monoculture="Mono")
combined1$type=factor(combined1$type)
table(combined1$type)
attach(combined1)
```

```{r}
library(ggplot2)
p<- ggplot(combined1, aes(x=factor(site), y=an_yield, fill=factor(type))) + 
  geom_boxplot()+labs(title="Annual yield of monocultures and mixtures by site",x="site", y = "Annual Yield")+theme_classic()
p
```




