---
title: "AgrodiversityData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AgrodiversityData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Getting started with **AgrodiversityData**

### Install and load the package
```{r setup}
library(AgrodiversityData)
```

### About the package
The agrodiversityData package allows to access to datasets of the 3 year continental scale Agrodiversity experiment that investigated plant diversity and ecosystem function in intensively-managed grassland communities across 17 countries. It was intended to see whether the experimental increases in plant diversity can increase the grassland outcomes. 

### Datasets included in the DImodels package
There are nine datasets included in the AgrodiversityData package: Site, Soil, Forage1, Forage2, Biomass1, Biomass2, Weather1, Weather2, combined. Details about each of these datasets is available in the corresponding help files. 

In this vignette, we will describe the Biomass1 dataset and show a worked analysis of it.

### The Biomass1 dataset
```{r}
data("Biomass1")
head(Biomass1)
```


### Exploring the dataset
```{r}
hist(Biomass1$Harv_yield, xlab = "Response", main = "")
```


### To obtain the summary statistics for the outcome
```{r}
summary(Biomass1$Harv_yield)
```






